Selective Sequential Model Selection

### 2015-12-07 paper.tex
minor edits, deleted comments, added discussion of computation for next-entry

\newcommand{\cM}{\mathcal{M}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\FDR}{\textnormal{FDR}}
\newcommand{\FCR}{\textnormal{FCR}}
\newcommand{\crt}{\phi}
\newcommand{\M}{\mathcal{M}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\cX}{\mathcal{X}}
\newcommand{\cV}{\mathcal{V}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\Gv}{\;\;\big|\;\;}
%\newcommand{\cP}{\mathcal{P}}
\newcommand{\proj}{\cP}
\newcommand{\pow}{\text{Pow}}
\newcommand{\supp}{\text{supp}}
\newcommand{\sF}{\mathscr{F}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\sC}{\mathscr{C}}
\newcommand{\hJ}{\widehat{J}}
\newcommand{\bH}{\mathbf{H}}
\newcommand{\bM}{\mathbf{M}}
\newcommand{\tM}{\widetilde{M}}
\newcommand{\tE}{\widetilde{E}}
\newcommand{\tV}{\widetilde{V}}
\newcommand{\tR}{\widetilde{R}}
\newcommand{\tL}{\widetilde{L}}
\newcommand{\hk}{\hat{k}}
\newcommand{\hr}{\hat{r}}       
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cJ}{\mathcal{J}}
\newcommand{\leqAS}{\overset{\textrm{a.s.}}{\leq}}
\newcommand{\Err}{\mathcal{E}}
\newcommand{\RSS}{\text{RSS}}

@@

\section{Introduction}
\label{sec:introduction}
Many model selection procedures produce a sequence of increasingly complex models, leaving the data analyst to choose among them. 
%While methods like cross-validation aim at minimizing out-of-sample prediction error, such methods tend to select a large fraction of noise variables. 
Given such a path, we consider the problem of choosing the simplest model in the path that is not falsified by the available data. Examples of path algorithms include forward stepwise linear regression, least angle regression (LAR) and the ever-active path in lasso ($\ell_1$-regularized) regression. \citet{taylor2014exact} study methods for generating exact $p$-values at each step of these path algorithms, and their methods provide a starting point for our proposals. Other related works include \citet{loftus2014significance}, who describe $p$-values for path algorithms that add groups of variables (instead of individual variables) at each step, and \citet{choi2014selecting}, who describe $p$-values for steps of principle components analysis (each step marking the estimation of a principle component direction).

@@

\begin{table}[ht]
\centering
\input{tables/diabetes_edit.tex}
\caption[tab:diab]{Forward stepwise regression for the diabetes data: naive $p$-values, $p$-values from the saturated model, and our max-$t$ $p$-values. The bold annotation in each column marks the model selected by ForwardStop with $\alpha=0.1$. For the max-$t$ $p$-values, this stopping rule gives exact FDR control at the 10\% level.}
\label{tab:diab}
\end{table}

@@

In the general setting, we observe data $Y \in \cY$ with unknown sampling distribution $F$, and then apply some algorithm to generate an adaptive sequence of $d$ nested statistical models contained in some {\em upper model} $M_{\infty}$:
\[
M_0(Y) \sub M_1(Y) \sub \cdots \sub M_d(Y) \sub M_\infty.
\]
\RJTcomment{Why does $M_0(Y)$ depend on $Y$ but $M_\infty$ does not?  I'm thinking of $M_0(Y)$ as the model with intercept, no?  For simplicity I've removed the dependence of $M_0$ on $Y$, but if I'm wrong about this, sorry, just change it back.} \\
\WFcomment{In many cases $M_0$ is deterministic but (for example) the way we define the ever-active path, we have $E_0(Y) = \bigcup_{\lambda\in\Lambda} \tE_\lambda(Y)$, which could be random if $\Lambda$ is a fixed grid. $M_\infty$ doesn't really need to be selected since we can just take it as a union over all possible models.}\\
By {\em model}, we mean a family of candidate probability distributions for $Y$. For example in  linear regression, a model specifies  the set of
predictors allowed to have nonzero coefficients (but not the  values of their coefficients). Note the ``assumption'' of an upper model involves no loss of generality --- we can always take $M_\infty$ as the union of all models under consideration. We will use the notation $M_{0:d}$ to denote the sequence $M_0, \ldots, M_d$, which we call the {\em model path}. We assume throughout that for each candidate model $M$ there is a minimal sufficient statistic $U(Y; \,M)$, and write
\[
U_k(Y) = U(Y; \,M_k(Y)).
\]
Given data $Y$ and model path $M_{0:d}$, we set ourselves the formal goal of selecting the simplest correct model: the smallest $k$ for which $F\in M_k(Y)$. Of course, in most real data problems all of the $M_k(Y)$ in the path, as well as all other models under consideration, are incorrect. In more informal terms, then, we seek the simplest model in the path that is not refuted by the available data.

@@

Following \citet{fithian2014optimal}, we say that for a fixed candidate null model $M$, the random variable $p_{k,M}(Y)$ is a valid {\em selective $p$-value} for $M$ at step $k$ if it is stochastically larger than uniform (henceforth super-uniform) under sampling from any $F\in M$, given that $M$ is selected. That is,
\begin{equation*}
\P_F\left(p_{k,M}(Y) \leq \alpha \mid M_{k-1}(Y) = M\right) 
\leq \alpha, \quad \forall F\in M, \; \alpha \in [0,1].
\end{equation*}
Once we have constructed selective $p$-values for each fixed $M$, we can use them as building blocks to construct a combined $p$-value for the random null $M_{k-1}(Y)$. Define
\[
p_k(y) = p_{k, M_{k-1}(y)}(y),
\]
which is super-uniform on the event $\{F \in M_{k-1}(Y)\}$:
\begin{equation}\label{eq:selectiveGuaranteePk}
\P_F\left(p_k \leq \alpha \mid F\in M_{k-1}\right) \leq \alpha, \quad \forall \alpha \in [0,1].
\end{equation}
One useful strategy for constructing exact selective tests is to condition on the sufficient statistics of the null model $M_{k-1}$. By sufficiency, the law
\[
\L(Y \;\mid\; U_{k-1}, \; M_{k-1}=M)
\]
is the same for every $F\in M$. Thus, we can construct selective tests by comparing the realized value of any test statistic $T(Y)$ to its known conditional distribution under the null. What remains is to choose the test statistic and compute its conditional null distribution, which can be challenging. See \citet{fithian2014optimal} for a general treatment. Section~\ref{sec:computation} discusses computational strategies for the tests we propose in this article.

@@

In this article we will concern ourselves primarily with testing the complete null, reflecting our stated aim of choosing the least complex model that is not rejected by the data. As we discuss further in Section~\ref{sec:selective-reg}, the saturated-model tests of \citet{taylor2014exact} are valid selective tests of $H_k^{\text{inc}}$. The advantage of these tests is that they are highly computationally efficient (they do not require sampling). But, unfortunately, they also carry a number of drawbacks: they require us to assume $\sigma^2$ is known, can result in a large reduction in power, create dependence between $p$-values at different steps, and are difficult to generalize beyond the case of linear regression. 
%See \citet{gsell2013false} for an in-depth discussion of the relative conceptual advantages and disadvantages between the three approaches.

@@

\RJTcomment{I've not changed anything with the notation below that conditions on $k_0=k$.  I'll leave it up to you Will, but as we discussed, I think it would be most useful to either write $P(p_k \leq \alpha | M_{k-1})$ on the set $\{ F \in M_{k-1}\}$, or to plainly explain what you mean by conditioning on an event involving $k_0$.} \\
In our problem setting, the sequence of selected models is random; thus, the truth or falsehood of each $H_k$ is not fixed, as assumed in the previous section. Trivially, we can recover the guarantees from the fixed setting if we construct our $p$-values conditional on the entire path $M_{0:d}(Y)$; however, this option is rather unappealing for both computational and statistical reasons. In this section we discuss what sort of conditional control the single-step $p$-values must satisfy to recover each of the guarantees in Section~\ref{sec:orderedProposals}.

@@

Define the {\em sufficient filtration} for the path $M_{0:d}$ as the filtration $\sF_{0:d}$ with 
\[
\sF_k = \sF(M_{0:k}, U_k).
\]
By our assumption of minimal sufficiency, $\sF_i \sub \sF_k$ for $i\leq k$.

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{.4\textwidth}
    % source code: bivariateSelVSat.R
    \includegraphics[width=\textwidth]{figs/bivariateSelVSat_powCurves_0.pdf}
    %\caption{\WFcomment{Write caption here.}}
    %\label{fig:bv_powCurves_0}
  \end{subfigure}
  \hspace{.1\textwidth}
  \begin{subfigure}[t]{.4\textwidth}
    % source code: bivariateSelVSat.R
    \includegraphics[width=\textwidth]{figs/bivariateSelVSat_powCurves_4.pdf}
    %\caption{\WFcomment{Write caption here.}}
  \end{subfigure}
  \caption{Power at level $\alpha=0.05$ for saturated- and selected-model tests at step 1, given that $j_1=1$. The power is plotted as a function of $\mu_1$, for two different values of $\mu_2$. When $\mu_2=0$, the selected-model test is strictly more powerful than the saturated-model test, but the difference is slight. By contrast, when $\mu_2=4$, the selected-model test is much more powerful. The dashed line shows $\alpha=0.05$.}
   \label{fig:bv_powCurves}
\end{figure}

@@

Until this point, we have deferred discussing how to compute the reference distribution for the max-$t$ test, next-entry test, or any of the other tests we have discussed. In each case, the $p$-value at step $k$ comes from a test that rejects when some test statistic $T_k$ is large compared to the law
\begin{equation}\label{eq:genDist}
\L(T_k(Y) \,\mid\, M_{k-1}(Y), U_{k-1}(Y)),
\end{equation}
under the null hypothesis that $F\in M_{k-1}$. Because $U_{k-1}$ is sufficient for $Y$ under the null, this law is completely known. Thus, we have reduced computation of the $p$-value at step $k$ to a sampling problem: if we can sample values of $Y$ from its null distribution given $M_{k-1}(Y), U_{k-1}(Y)$, we can numerically approximate the $p$-value to whatever precision we desire.

@@

@@

\begin{figure}[h]
  \centering
  % source code: ??? for simulation, sparseSim.R for plotting
  \includegraphics[width=1\textwidth]{figs/simulation_snr_5_alpha_05_null_false.pdf}
  \caption{  CDFs of nominal (black), max-$z$ (red), max-$t$ (green) and  saturated-model (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on testing a false null hypothesis at step $k$. The max-$t$ approaches are much more powerful than the saturated-model test. The nominal test appears to be powerful, 
  but is not $U[0,1]$ under the null, as shown below in Figure \ref{fig:simulation_null_true}.}
  \label{fig:simulation_null_false}
\end{figure}

\begin{figure}[h]
  \centering
  % source code: ??? for simulation, sparseSim.R for plotting
  \includegraphics[width=1\textwidth]{figs/simulation_snr_5_alpha_05_null_true.pdf}
  \caption{  CDFs of nominal (black), max-$z$ (red), max-$t$ (green) and  saturated-model (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on testing a true null hypothesis at step $k$.  The nominal test is badly anti-conservative, while all of the other methods  show uniform $p$-values as desired.}
  \label{fig:simulation_null_true}
\end{figure}

\begin{figure}[h]
  \centering
  % source code: ??? for simulation, sparseSim.R for plotting
  \includegraphics[width=1\textwidth]{figs/simulation_snr_5_alpha_05_noise_var.pdf}
  \caption{ CDFs of nominal (black), max-$z$ (red), max-$t$ $\sigma$ (green) and  saturated-model (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on the event that the variable added at step $k$ is a noise variable in the full model. Here, none of the methods produce uniform $p$-values. The null hypothesis is false in most cases and so --- in our model-centric point of view --- rejection is the desired outcome.}
  \label{fig:simulation_noise_var}
\end{figure}

@@

\subsection{Decision Trees}
In this section we discuss another application of adaptive sequential inference, to binary decision trees. Specifically, the classification and regression tree  (CART)  method builds a decision tree in a top down manner, finding the best available split at each node \citep{breiman1984classification}.  When considering splitting two daughter nodes, the generic CART algorithm splits the nodes in an arbitrary order, only stopping when a node reaches a minimum size.  We instead consider a  special version of CART: the ``best first'' method, which orders splits by their achieved reduction in loss. This procedure is used, for example in the R package for gradient boosting, called {\tt gbm}. The best-first algorithm is thus a sequential selection  procedure, to which we can apply the results in this paper. Hence we can obtain independent, sequential $p$-values for each successive split in the decision tree. \RJTcomment{Just for what it's worth, I always think of CART as performing best-first splits.  This is how Jerry teaches it, at least.}

@@

Open-source code is available at this article's github repository at \texttt{github.com/wfithian/sequential-selection}. R and Python code are available to implement proposals in this paper are available at \texttt{github.com/selective-inference}.

@@

\JTcomment{I don't really see the point of Figure 5. It is abundandtly clear
that if feasible an IID sample is preferable over an MCMC sample. It is
just as easy to make plots where accept/reject will take forever to get even one sample point.}

>>>>

\newcommand{\cM}{\mathcal{M}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\FDR}{\textnormal{FDR}}
\newcommand{\FCR}{\textnormal{FCR}}
\newcommand{\crt}{\phi}
\newcommand{\M}{\mathcal{M}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\cX}{\mathcal{X}}
\newcommand{\cV}{\mathcal{V}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\Gv}{\;\;\big|\;\;}
\newcommand{\proj}{\cP}
\newcommand{\pow}{\text{Pow}}
\newcommand{\supp}{\text{supp}}
\newcommand{\sF}{\mathscr{F}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\sC}{\mathscr{C}}
\newcommand{\hJ}{\widehat{J}}
\newcommand{\bH}{\mathbf{H}}
\newcommand{\bM}{\mathbf{M}}
\newcommand{\tM}{\widetilde{M}}
\newcommand{\tE}{\widetilde{E}}
\newcommand{\tV}{\widetilde{V}}
\newcommand{\tR}{\widetilde{R}}
\newcommand{\tL}{\widetilde{L}}
\newcommand{\hk}{\hat{k}}
\newcommand{\hr}{\hat{r}}       
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cJ}{\mathcal{J}}
\newcommand{\leqAS}{\overset{\textrm{a.s.}}{\leq}}
\newcommand{\Err}{\mathcal{E}}
\newcommand{\RSS}{\text{RSS}}

@@

\section{Introduction}
\label{sec:introduction}
Many model selection procedures produce a sequence of increasingly complex models, leaving the data analyst to choose among them. 
Given such a path, we consider the problem of choosing the simplest model in the path that is not falsified by the available data. Examples of path algorithms include forward stepwise linear regression, least angle regression (LAR) and the ever-active path in lasso ($\ell_1$-regularized) regression. \citet{taylor2014exact} study methods for generating exact $p$-values at each step of these path algorithms, and their methods provide a starting point for our proposals. Other related works include \citet{loftus2014significance}, who describe $p$-values for path algorithms that add groups of variables (instead of individual variables) at each step, and \citet{choi2014selecting}, who describe $p$-values for steps of principle components analysis (each step marking the estimation of a principle component direction).

@@

\begin{table}[ht]
\centering
{\small \input{tables/diabetes_edit.tex}}
\caption[tab:diab]{Forward stepwise regression for the diabetes data: naive $p$-values, $p$-values from the saturated model, and our max-$t$ $p$-values. The bold annotation in each column marks the model selected by ForwardStop with $\alpha=0.1$. For the max-$t$ $p$-values, this stopping rule gives exact FDR control at the 10\% level.}
\label{tab:diab}
\end{table}

@@

In the general setting, we observe data $Y \in \cY$ with unknown sampling distribution $F$, and then apply some algorithm to generate an adaptive sequence of $d$ nested statistical models contained in some {\em upper model} $M_{\infty}$:
\[
M_0(Y) \sub M_1(Y) \sub \cdots \sub M_d(Y) \sub M_\infty.
\]
By {\em model}, we mean a family of candidate probability distributions for $Y$. For example in  linear regression, a model specifies  the set of
predictors allowed to have nonzero coefficients (but not the  values of their coefficients). Note the ``assumption'' of an upper model involves no loss of generality --- we can always take $M_\infty$ as the union of all models under consideration. We will use the notation $M_{0:d}$ to denote the sequence $M_0, \ldots, M_d$, which we call the {\em model path}. We assume throughout that for each candidate model $M$ there is a minimal sufficient statistic $U(Y; \,M)$, and write
\[
U_k(Y) = U(Y; \,M_k(Y)).
\]
Given data $Y$ and model path $M_{0:d}$, we set ourselves the formal goal of selecting the simplest correct model: the smallest $k$ for which $F\in M_k(Y)$. Of course, in most real data problems all of the $M_k(Y)$ in the path, as well as all other models under consideration, are incorrect. In more informal terms, then, we seek the simplest model in the path that is not refuted by the available data.

@@

Following \citet{fithian2014optimal}, we say that for a fixed candidate null model $M$, the random variable $p_{k,M}(Y)$ is a valid {\em selective $p$-value} for $M$ at step $k$ if it is stochastically larger than uniform (henceforth super-uniform) under sampling from any $F\in M$, given that $M$ is selected. That is,
\begin{equation*}
\P_F\left(p_{k,M}(Y) \leq \alpha \mid M_{k-1}(Y) = M\right) 
\leq \alpha, \quad \forall F\in M, \; \alpha \in [0,1].
\end{equation*}
Once we have constructed selective $p$-values for each fixed $M$, we can use them as building blocks to construct a combined $p$-value for the random null $M_{k-1}(Y)$. Define
\[
p_k(y) = p_{k, M_{k-1}(y)}(y),
\]
which is super-uniform on the event $\{F \in M_{k-1}(Y)\}$:
\begin{equation}\label{eq:selectiveGuaranteePk}
\P_F\left(p_k \leq \alpha \mid F\in M_{k-1}\right) \leq \alpha, \quad \forall \alpha \in [0,1].
\end{equation}
One useful strategy for constructing exact selective tests is to condition on the sufficient statistics of the null model $M_{k-1}$. By sufficiency, the law
\[
\L_F(Y \;\mid\; U_{k-1}, \; M_{k-1}=M)
\]
is the same for every $F\in M$. Thus, we can construct selective tests and $p$-values by comparing the realized value of any test statistic $T_k(Y)$ to its known conditional distribution under the null. It remains only to choose the test statistic and compute its conditional null distribution, which can be challenging. See \citet{fithian2014optimal} for a general treatment. Section~\ref{sec:computation} discusses computational strategies for the tests we propose in this article.

@@

In this article we will concern ourselves primarily with testing the complete null, reflecting our stated aim of choosing the least complex model that is not rejected by the data. As we discuss further in Section~\ref{sec:selective-reg}, the saturated-model tests of \citet{taylor2014exact} are valid selective tests of $H_k^{\text{inc}}$. The advantage of these tests is that they are highly computationally efficient (they do not require sampling). But, unfortunately, they also carry a number of drawbacks: they require us to assume $\sigma^2$ is known, can result in a large reduction in power, create dependence between $p$-values at different steps, and are difficult to generalize beyond the case of linear regression.

@@

In our problem setting, the sequence of selected models is random; thus, the truth or falsehood of each $H_k$ is not fixed, as assumed in the previous section. Trivially, we can recover the guarantees from the fixed setting if we construct our $p$-values conditional on the entire path $M_{0:d}(Y)$; however, this option is rather unappealing for both computational and statistical reasons. In this section we discuss what sort of conditional control the single-step $p$-values must satisfy to recover each of the guarantees in Section~\ref{sec:orderedProposals}.

@@

Define the {\em sufficient filtration} for the path $M_{0:d}$ as the filtration $\sF_{0:d}$ with 
\[
\sF_k = \sF(M_{0:k}, U_k),
\]
where $\sF(Z)$ denotes the $\sigma$-algebra generated by random variable $Z$. By our assumption of minimal sufficiency, $\sF_i \sub \sF_k$ for $i\leq k$.

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{.4\textwidth}
    % source code: bivariateSelVSat.R
    \includegraphics[width=\textwidth]{figs/bivariateSelVSat_powCurves_0.pdf}
  \end{subfigure}
  \hspace{.1\textwidth}
  \begin{subfigure}[t]{.4\textwidth}
    % source code: bivariateSelVSat.R
    \includegraphics[width=\textwidth]{figs/bivariateSelVSat_powCurves_4.pdf}
  \end{subfigure}
  \caption{Power at level $\alpha=0.05$ for saturated- and selected-model tests at step 1, given that $j_1=1$. The power is plotted as a function of $\mu_1$, for two different values of $\mu_2$. When $\mu_2=0$, the selected-model test is strictly more powerful than the saturated-model test, but the difference is slight. By contrast, when $\mu_2=4$, the selected-model test is much more powerful. The dashed line shows $\alpha=0.05$.}
   \label{fig:bv_powCurves}
\end{figure}

@@

Until this point, we have deferred discussing how to compute the reference distribution for the max-$t$ test, next-entry test, or any of the other tests we have discussed. In each case, the $p$-value at step $k$ comes from a test that rejects when some test statistic $T_k$ is large compared to the law
\begin{equation}\label{eq:genDist}
\L(T_k(Y) \,\mid\, M_{k-1}(Y), U_{k-1}(Y)),
\end{equation}
under the null hypothesis that $F\in M_{k-1}$. Because $U_{k-1}$ is sufficient for $Y$ under the null, this law is completely known. Thus, we have reduced computation of the $p$-value at step $k$ to a sampling problem: if we can sample values of $Y$ from its null distribution given $M_{k-1}(Y), U_{k-1}(Y)$, and compute the test statistic $T_k(Y)$ for each sample, we can numerically approximate the $p$-value to whatever precision we desire.

@@

\subsection{Computing the Next-Entry $p$-Values}\label{sec:next-entry-comp}

For the next entry test, the test statistic $\lambda_k(Y)$ is a function of the regularization path. A na\"{i}ve algorithm would simply recompute the entire path for each new sample $Y^*$ from the conditional null distribution in~\eqref{eq:genDist}. However, if we are a bit more clever, we can avoid ever recomputing the path.

Let $A$ denote the event $\{E_{k-1}=E, U_{k-1}=u\}$, and let $Y^*$ represent a sample from $F$, independent of $Y$. On $A$, the next-entry $p$-value $p_k$ may be written as
\begin{align}
  p_k(Y) 
  &= \P(\lambda_k(Y^*) > \lambda_k(Y) \mid E_{k-1}(Y^*)=E, M_{k-1}(Y^*)=u)\\
  &= 1 - \P\left( \bigcup_{\lambda > \lambda_k(Y)} \{\hat\theta^\lambda(Y^*) = \hat\theta^{(E, \lambda)}(Y^*)\} \mid E_{k-1}(Y^*)=E, U_{k-1}(Y^*)=u\right) \\
  &= 1 - \P\left( \bigcup_{\lambda > \lambda_k(Y)} \hat\theta^\lambda(Y^*) = \hat\theta^{\lambda}(Y) \mid E_{k-1}(Y^*)=E, U_{k-1}(Y^*)=u\right),
\end{align}
where the third equality is justified by the fact that $\hat\theta^{(E, \lambda)}$ depends only on $U_E$, and $\hat\theta^{(E,\lambda)}(Y)=\hat\theta^\lambda(Y)$ for $\lambda > \lambda_k(Y)$. As a result, we do {\em not} need to compute the whole path for each new $Y^*$; instead, we only need to compute the regularization path for $Y$, and then check for each $\lambda > \lambda_k(Y)$ whether $\hat\theta^\lambda(Y)$ is also optimal for $Y^*$. If $-\ell$ and $P_\lambda$ are both convex, then, we merely need to verify the Karush-Kuhn-Tucker (KKT) conditions.

\paragraph{Remark} If $\lambda_k$ has a discrete distribution --- as it would, for example, if $\Lambda$ is a discrete grid --- then we can either accept that $p_k$ is conservative, or randomize $p_k$ so it is exactly uniform under the null. For a randomized $p_k$, we also need the probability $\lambda_k(Y^*)$ {\em equals} $\lambda_k(Y)$, which requires computing $\hat\theta^{(E, \lambda_k)}(Y)$ and checking whether $\hat\theta^{(E, )}$.

@@

\begin{figure}[h]
  \centering
  % source code: compare_methods.py for simulation, sparseSim_figs.R for plotting
  \includegraphics[width=1\textwidth]{figs/simulation_snr_5_alpha_05_null_false.pdf}
  \caption{  CDFs of nominal (black), max-$z$ (red), max-$t$ (green) and  saturated-model (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on testing a false null hypothesis at step $k$. The max-$t$ approaches are much more powerful than the saturated-model test. The nominal test appears to be powerful, 
  but is not $U[0,1]$ under the null, as shown below in Figure \ref{fig:simulation_null_true}.}
  \label{fig:simulation_null_false}
\end{figure}

\begin{figure}[h]
  \centering
  % source code: compare_methods.py for simulation, sparseSim_figs.R for plotting
  \includegraphics[width=1\textwidth]{figs/simulation_snr_5_alpha_05_null_true.pdf}
  \caption{  CDFs of nominal (black), max-$z$ (red), max-$t$ (green) and  saturated-model (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on testing a true null hypothesis at step $k$.  The nominal test is badly anti-conservative, while all of the other methods  show uniform $p$-values as desired.}
  \label{fig:simulation_null_true}
\end{figure}

\begin{figure}[h]
  \centering
  % source code: compare_methods.py for simulation, sparseSim_figs.R for plotting
  \includegraphics[width=1\textwidth]{figs/simulation_snr_5_alpha_05_noise_var.pdf}
  \caption{ CDFs of nominal (black), max-$z$ (red), max-$t$ $\sigma$ (green) and  saturated-model (blue) $p$-values in the simulation of Section~\ref{sec:sparseReg}, conditional on the event that the variable added at step $k$ is a noise variable in the full model. Here, none of the methods produce uniform $p$-values. The null hypothesis is false in most cases and so --- in our model-centric point of view --- rejection is the desired outcome.}
  \label{fig:simulation_noise_var}
\end{figure}

@@

\subsection{Decision Trees}
In this section we discuss another application of adaptive sequential inference, to binary decision trees. Specifically, the classification and regression tree  (CART)  method builds a decision tree in a top down manner, finding the best available split at each node \citep{breiman1984classification}.  When considering splitting two daughter nodes, the generic CART algorithm splits the nodes in an arbitrary order, only stopping when a node reaches a minimum size.  We instead consider a  special version of CART: the ``best first'' method, which orders splits by their achieved reduction in loss. This procedure is used, for example in the R package for gradient boosting, called {\tt gbm}. The best-first algorithm is thus a sequential selection  procedure, to which we can apply the results in this paper. Hence we can obtain independent, sequential $p$-values for each successive split in the decision tree.

@@

Open-source code is available at this article's github repository at:\\ \texttt{github.com/wfithian/sequential-selection}.

R and Python code are available to implement proposals in this paper are available at:\\ \texttt{github.com/selective-inference}.

@@
